Some Graphical Realizations of Two-Row Specht Modules of Iwahori--Hecke Algebras of the Symmetric Group

### 2019-07-30 tex/Drafts/Draft-2.tex

  \fakesubsection{Crossingless Matchings}
  The following definition modifies the crossingless matchings defined by Khovanov.\cite{Khovanov}

@@

  \def\vara{\alpha_1}
  \def\varb{\alpha_2}
  \def\varc{\varepsilon_1}
  \def\vard{\delta}
  \def\vare{\varepsilon_2}
  \def\vs{\texttt{*}}
  \def\vp{\texttt{0}}
  \fakesubsection{Fibonacci Representation}
  Now suppose that $e = 5$ and $k$ contains the algebraic number $\sqrt{q + q^4}$ for reasons which will be apparent soon.
  For convenience set $m := 2n + 4$.
  The following is a modification of Shor--Jordan's Fibonacci representation of the braid group.\cite{Shor}

@@

  \fakesubsection{Overview of Paper}

@@

\section{Preliminaries on Specht Modules}\label{Specht Modules Section}
  For this section and the rest of the paper, assume $n > 0$.

@@

  \begin{figure}
  \ytableausetup{mathmode,boxsize=4.5em}
  \begin{ytableau}
    n+r+1 & n + r & \dots & r + 2 & r & r-1 & \dots & 1\\ 
    n & n-1 & \dots & 1
  \end{ytableau}
  \ytableausetup{mathmode,boxsize=normal}
  \caption{The young diagram corresponding to the partition $(n+r,n)$ with filled-in ook lengths.}\label{Hooks}
\end{figure}

  From part (i) we see that irreducibility at $e > n$ is not dependent on $p$, and we may cover many modular cases without reference to the characteristic of $k$.
  We will finish our discussion of irreducibility of $S^\lambda$ via sharp characterization of the $e \leq n$ case.
  \begin{corollary}
    If $r = 0$, assume $e > 2$.
    Suppose $e \leq n$, and suppose $p > n + r + 1$.
    Then, $S^{(n+r,n)}$ is irreducible if and only if $e \mid r+1$.
  \end{corollary}
  \begin{proof}
    This follows from the proof of Corollary \ref{S irreducibility} part (ii) and the fact that $\nu_p(h) = \nu_p(h')$ for all naturalls $h,h'$. 
  \end{proof}
  \subsection{Branching}
  In this section as well as later sections, we will consider the restriction of representations of $\SH$ to particular subalgebras isomorphic to $\SH_{k,q}\prn{S_{2n + r - 1}}$.
  We verify in Appendix \ref{Algebra} that any two subalgebras of $\SH$ generated by $2n + r - 2$ simple transpositions are canonically isomorphic, and the corresponding restrictions are canonically isomorphic via this isomorphism of algebras.
  We will hence abuse notation, pick one such subalgebra $\SH'$, and notate $\Res_{\SH'}^\SH W$ by $\Res W$ for any $\SH$-module $W$.

@@

  Now that we've characterized how $D^\lambda$ restrict, we can describe how strongly these restrictions characterize irreducibles.
  Namely, we will prove that some $D^\lambda$ having the same composition series as  $D^{(n+r,n)}$ is sufficient to determine that $\lambda = (n+r,n)$ in the case that condition (i) of Corollary \ref{S irreducibility} holds and either $r \neq 0$ or $e \neq 4$.
  \begin{proposition}\label{Combinatorics}
    Let $\lambda$ be an $e$-regular partition of $2n + r$.
    \begin{enumerate}[label={(\roman*)}]
      \item Suppose $r > 0$, suppose $e \nmid r+1, r + 2,\dots,n + r + 1$, and suppose either $e \mid r$ or $e \nmid r-2$.
        If $D^\lambda$ has the composition series 
        \begin{equation}\label{D Composition Series}
          0 \subset D^{(n+r-1,n)} \subset \Res \, D^{\lambda}
        \end{equation}
        with factor $\Res \, D^{\lambda} / D^{(n+r-1,n)} \simeq D^{(n+r,n)}$, then $\lambda = (n+r,n)$.
      \item Suppose $r = 0$, suppose $e \nmid 4$, and suppose $D^{(n,n-1)} \simeq \Res \, D^\lambda$.
        Then $\lambda = (n,n)$. 
    \end{enumerate}
  \end{proposition}
  \begin{proof}
    Note that $e > n$.
    Further, note that the above characterizations are necessary regardless of $e$-regularity;
    in the case that $\mu$ below fails too be $e$-regular, this proposition will prove that $\lambda$ does not satisfy \label{D Composition Series}, a contradiction.

@@

\section{Crossingless Matchings and Specht Modules}\label{Crossingless Matchings Section}
In the following section, we will analyze the crossingless matchings representation $M_{2n + r}^r$ with the goal of proving $M_{2n + r}^r \simeq S^{(n+r,n)}$ whenever possible.
We begin by proving irreducibility of $M_{2n + r}^r$ in all cases that $(n+r,n)$ is $e$ top-indivisible;
when $p = 2$, this is all cases where $S^{(n+r,n)}$ is irreducible.
This is proven via an inductive process; if $e \nmid n + r + 1$, then $M$ contains no sign subrepresentation, and this allows us to ``project'' down to the case $M_{2(n-1) + r}^r$, and prove irreducibility of $M$ from irreducibility of this space.

\subsection{Irreducibility of $M$}
\begin{lemma}
  \label{Cyclic}
  Every basis vector in $M_{2n + r}^r$ is cyclic.
\end{lemma}
\begin{proof}
  We have already proven this in the $r = 0$ case, so suppose that $r > 0$.

    Note that, between anchors $a<a'$ having no arc $b$ with $a < b < a'$, the $M_{a'-a}^0$ case allows us to generate the vector with all length-2 arcs between $a,a'$ and identical arcs/anchors outside of this sub-matching.\footnote{At the ends, we apply the $M_a^0$ case or the $M_{2n + r - a}^{0}$ case in the same way for the first $a$ or last $2n + r - a$ indices.}

  Applying this between each arc gives us a vector with length-2 arcs and anchors, and we may use the appropriate $(1+T_i)$ to move anchors to any positions, and the reverse process from above to generate the correct matchings between arcs and generate any other basis vector.
\end{proof}

Let $K := \bigcap_{i=1}^{2n+r-1} \ker (1 + T_i) = \ker \bigoplus_{i = 1}^{2n + r - 1} (1 + T_i)$.
This will be a large technical tool in our proof of irreducibility.

\iffalse
\begin{lemma}\label{Represented}
  Let $w_j$ be the basis vector with anchors $1,\dots,r$ and all arcs of maximal length.
  Suppose $w \in K \backslash \cbr 0$.
  Then, $w_j$ is represented in $w$.
\end{lemma}
\begin{proof}
  We will show this in steps; first, we show that, given that a vector is represented with anchors $1,\dots,s$, there must be a vector represented in $w$ with $(s+1)$st anchor, including when $s = 0$;
  this implies that a vector is represented with anchors $1,\dots,r$.
  Then, we will show that, given a vector is represented with anchors $1,\dots,r$ and first $s$ arc-lengths $n,n-2,\dots,n-2s$, there is a vector represented with these and the $(s+1)$st arc-length $n-2s-2$.
  This implies that $w_j$ is represented.

  \def\lemsep{7pt}
  \vspace{\lemsep}
  \textit{Step 1.}
  Suppose that $s < r$ is the maximal number such that a vector with anchors $1,\dots,s$ is represented.
  Take the vector $w_i$ which, among vectors represented in $w$ with anchors $1,\dots,s$, has $(s+1)$st anchor at minimal index $t > s + 1$,
  Then, $q^{-1/2}(1 + T_{t-1})w_i$ has anchors $1,\dots,s$ and a earlier index than $t$, so it was not represented before;
  further, for any other basis vector $w_l \neq w_i$ to map onto $q^{-1/2}(1 + T_{t-1})w_i$, we would require that $w_l$ has anchors $1,\dots,s$ and some other anchor at index $t' < t$, so it is not represented.
  Hence $w_i$ is unique among the vectors represented mapping onto $q^{-1/2}(1 + T_{t-1})w_i$, and $(1 + T_{t-1})w$ represents this vector, giving $w \notin \ker (1 + T_{t-1})$.

  When $s = 0$, this is similar, and we simply perform this logic on the 1st anchor.
  Each lead to contradiction, so we must have $s = r$.

  \vspace{\lemsep}
  \textit{Step 2.}
  This step is similar;
  suppose that $s < n$ is the maximal number such that a vector with anchors $1,\dots,r$ and first $s$ arc-lengths $n,\dots,n-2s$ is represented.
  Take the vector $w_i$ which, among vectors represented in $w$ with anchors $1,\dots,r$ and first $s$ arc-lenths $n,\dots,n-2s$, has maximal length $t$ of the arc beginning at index $r + s + 1$.
  Then, $q^{1/2}(1 + T_{r + s + t})w_i$ is mapped to only by $w_i$ and vectors having anchors $1,\dots,r$ and first $s+1$ arc-lengths $n,\dots,n-2s,t'$ with $t' > t$, which are not represented in $w$;
  hence $q^{-1/2}(1 + T_{r + s + t})w_i$ is represented in $(1 + T_{r+s+t})w$, giving $w \notin \ker (1 + T_{r + s + t})$.
  The $s = 0$ case is similar, and implies that $s = n$.
\end{proof}
\fi

\begin{lemma}\label{Trivial}
  Suppose $e \nmid n + r + 1$.
  Then, $K = 0$.
\end{lemma}
\begin{proof}[Proof 1.]
  Consider the matrix $A = \bigoplus (1 + T_i)$ having kernel $K$.
  It is sufficient by lemma \ref{Represented} to show that $A$ includes a row $[0,\dots,0,1,0,\dots,0]$ with a nonzero entry only on the row $j$.

@@

  We may prove invertibility of this matrix by proving that $\det B_{n + r} = \brk{n + r + 1}_q$ inductively on $n+r$.
  This is satisfied for our base case $n + r = 1$, so suppose that it is true for each $m < n + r$.
  Then,
  \begin{align*}
    \det B_{n+r} &= (q + 1) \det B_{n + r - 1} - q \det B_{n + r - 2}\\
    &= (q + 1)(1 + \dots + q^{n + r - 1}) - (q + \dots + q^{n + r - 1})\\
    &= 1 + \dots + q^{n + r}\\
    &= \brk{n + r + 1}_q.
  \end{align*}
  Hence $\det B_{n + r} \neq 0$, and $K = 0$.
\end{proof}
\begin{theorem}\label{Irreducibility Theorem}
  Suppose that $e \nmid r+2,r+3,\dots,n+r+1$.
  Then, the representation $M_{2n + r}^r$ is irreducible. 
\end{theorem}
\begin{proof}
  We proceed by induction on $n$.
  Note that, by identification with the trivial and sign representation, the base case $n = 0$ is already proven.

  Take an arbitrary vector $w \in W$.
  By Lemma \ref{Trivial} there exists some $(1 + T_i) \in \SH$ such that $(1 + T_i)w$.
  Note that \[\ima (1 + T_i) = \Span\cbr{w_j \mid w_j \text{ contains arc }(i,i+1)}.\]
  Hence, as vector spaces, there is an isomorphism $\varphi:\ima(1 + T_i) \rightarrow M_{2(n-1) + r}^r$ ``deleting'' the arc $(i,i+1)$.

  We will show that, for every action $(1 + T_j') \in \SH(S_{2(n-1) + r})$, there is some action $h_j \in M_{2n + r}^r$ such that the following commutes:
  \[
    \begin{tikzcd}
      \ima (1 + T_i) \arrow[r,"\varphi" above, "\sim" below] \arrow[d,"h_j"] & M_{2(n-1) + r}^r \arrow[d,"1 + T_j"]\\
      \ima (1 + T_i) \arrow[r,"\varphi" above, "\sim" below] & M_{2(n-1) + r}^r
    \end{tikzcd}
  \]
  Indeed, when $i \neq j$ this is given by $h_j = 1 + T_j$, and we have $h_i = q^{-1}(1 + T_i)(1 + T_{i+1})(1 + T_{i-1})$, as given by Figure \ref{bigloop}.

  Note that, by definition, $e \nmid r+2,\dots,n+r$ as well, and hence $(n+r-1,n-1)$ satisfies the hypotheses of the proposition as well..
  Then, due to the inductive hypothesis, there is some action $h' \in \SH(S_{2(n-1) + r})$ sending $\varphi((1 + T_i)w)$ to the image of a basis vector;
  then, the action $\SH$ generates the endomorphism $\varphi^{-1}h'\varphi$ sending $(1 + T_i)w$ to a basis vector, giving $w$ cyclic and hence $M_{2n + r}^r$ irreducible.
  \begin{figure}
  \begin{adjustbox}{width=\textwidth}
    \Action{6}{1/6, 2/5, 3/4}{2}{1/6, 2/3, 4/5 }{q^{1/2}} \hspace{20pt} 
    \IsoAction{8}{1/8, 2/7, 3/4, 5/6}{3}{1/8, 2/5, 3/4, 6/7}{q^{1/2}}
  \end{adjustbox}
  \begin{adjustbox}{width=\textwidth}
    \Action{4}{1/4, 2/3}{2}{1/4,2/3}{(1 + q)} \hspace{20pt}
    \IsoAction{6}{1/6, 2/5, 3/4}{3}{1/6, 2/5, 3/4}{(1 + q)}
\end{adjustbox}
  \caption{The correspondence between the action of $(1 + T_2)$ on $w'_5 \in M^0_6$ and the action of $q^{-1}(1 + T_3)(1 + T_4)(1 + T_2)$ on the corresponding vector in $M^0_8$ having arc $(3,4)$ first, then on $w'_2 \in M^0_4$.
  This demonstrates that the action works with and without creating a loop.
  }
  \label{bigloop}
  \end{figure}
\end{proof}

\subsection{Correspondence}
The following theorem of Mathas generalizes the characteristic-free version of the classical branching theorem.\cite{Mathas-article}
It will not be necessary for our present proof of the correspondence, but analogy with $M$ is suggestive.
\begin{theorem}[Characteristic-Free Classical Branching Theorem]
  Let $\lambda$ be a partition of $m$ with $\ell$ removable nodes.
  Then, $\Res \, S^\lambda$ has an $\SH_{k,q}(S_{m-1})$-module filtration
  \[
    0 = S^{0,\lambda} \subset S^{1,\lambda} \subset \cdots \subset S^{\ell,\lambda} = \Res S^\lambda
  \]
  such that $S^{t,\lambda} / S^{t-1,\lambda} \simeq S^{\lambda(t)}$ for all $1 \leq t \leq \ell$.\qed
\end{theorem}

If we replace $S^\lambda$ with the appropriate $M_{2n + r}^r$ above, we find the statement of the following proposition.
\begin{proposition}Suppose that $n > 0$.

  \begin{enumerate}[label={(\roman*)}]
    \item
    Suppose that $r > 0$.
    Then, a filtration of $\Res M_{2n + r}^r$ is given by
    \begin{equation}
      0 \subset M_{2n + r - 1}^{r-1} \subset \Res \, M_{2n + r}^r \label{Filtration}
     \end{equation}
     with $\Res \, M_{2n + r}^r / M_{2n + r - 1}^{r-1} \simeq M_{2n + r - 1}^{r + 1}$. 
    \item
      We have the following isomorphism of representations:
      \begin{equation}
        M_{2n - 1}^1 \simeq \Res \; M_{2n}^0 \label{0 Restriction}
       \end{equation}
  \end{enumerate}
    When the case is type (i) from the irreduibility lemma, this is a composition series.
\end{proposition}
\begin{proof}
  \textbf{(i)}
  Note that we may identify the subrepresentation of $\Res \; M_{2n + r}^r$ having anchor $n$ with $M_{2n + r - 1}^{r-1}$.

  Let $U := \Res \; M_{2n + r}^r / M_{2n + r - 1}^{r - 1}$. 
  Let $\phi:U \rightarrow M_{2n + r - 1}^{r + 1}$ be the $k$-linear map which regards the arc $(i,2n + r)$ in $U$ as an anchor at $i$ in $M_{2n + r - 1}^{r + 1}$.
  It is not hard to verify that this is a well-defined isomorphism of vector spaces, so we must show that it is $\SH$-linear.

  Given a basis vector $w_j$ with arc $(i,2n + r)$, $\phi$ is clearly compatible with $T_{i'}$ with $i' \neq i,i-1$.
  Further, it's easy to verify that $\phi$ is compatible with $T_{i}$ and $T_{i-1}$, as actions on one anchor were designed for this deformation.
  When there are anchors $(i,i+1)$, then $\phi(T_iw_j) = T_i\phi(w_j) = 0$, and similar for $T_{i -1}$.
  Hence $\phi$ is an isomorphism of representations, and the statement is proven.

  \textbf{(ii)}
  This follows with the above proof, defining $M_{2n - 1}^{-1} := 0$
\end{proof}

We've now assembled the basic pieces necessary to prove our correspondence in the case $e > n + r  1$.
Due to some problematic phenomena in the $r = 0$ case, we will initially make an assumption that $e \neq 4$ or $r \neq 0$ so that we may use the combinatorics of Proposition \ref{Combinatorics}.
We will then assume the remaining case $e = 4, r = 0$, and prove our correspondence using process of elimination via the other surrounding cases for $e = 4$.

\begin{theorem}\label{Correspondence Theorem}
  Suppose $e > n + r + 1$.
  Then, $M_{2n + r}^r \simeq S^{(n+r,n)}$.
\end{theorem}
\begin{proof}
  The case $n = 0$ is already proven, so suppose $n > 0$.
  In order to use Proposition \ref{Combinatorics}, suppose for now that either $e \nmid 4$ or $r \neq 0$.

  We will prove this inductively; by identification with the trivial and sign representations, the $2n + r = 2$ caseholds, so suppose this is true for $M_{2m + s}^s$ whenever $2m + s < 2n + r$ and $m + s \leq n + r$ (i.e. $e > m + s + 1$).

  By irreducibility, we know that $M_{2n + r}^r \simeq D^\lambda$ for some $e$-restricted partition $\lambda$.
  By the inductive hypothesis and irreducibility, we have a composition series given by the exact sequence
  \begin{equation}
    \label{Composition Series} 0 \longrightarrow D^{(n + r - 1,n)} \longrightarrow \Res \, D^\lambda \longrightarrow D^{(n+r,n-1)} \longrightarrow 0
   \end{equation}
  Hence the theorem is given by Proposition \ref{Combinatorics}.

>>>>

  \fakesubsection{Crossingless matchings}
  The following definition modifies the crossingless matchings defined by Khovanov.\cite{Khovanov}

@@

  \def\vara{\alpha_1}
  \def\varb{\alpha_2}
  \def\varc{\varepsilon_1}
  \def\vard{\delta}
  \def\vare{\varepsilon_2}
  \def\vs{\texttt{*}}
  \def\vp{\texttt{0}}
  \fakesubsection{Fibonacci representation}
  Now suppose that $e = 5$ and $k$ contains the algebraic number $\sqrt{q + q^4}$ for reasons which will be apparent soon.
  For convenience set $m := 2n + 4$.
  The following is a modification of Shor--Jordan's Fibonacci representation of the braid group.\cite{Shor}

@@

  \fakesubsection{Overview of paper}

@@

\section{Preliminaries on Specht modules}\label{Specht Modules Section}
  For this section and the rest of the paper, assume $n > 0$.

@@

  \begin{figure}
  \ytableausetup{mathmode,boxsize=4.5em}
  \begin{ytableau}
    n+r+1 & n + r & \dots & r + 2 & r & r-1 & \dots & 1\\ 
    n & n-1 & \dots & 1
  \end{ytableau}
  \ytableausetup{mathmode,boxsize=normal}
  \caption{The young diagram corresponding to the partition $(n+r,n)$. The hook lengths are in the center of the corresponding cells.}\label{Hooks}
\end{figure}

  From part (i) we see that irreducibility at $e > n$ is not dependent on $p$, and we may cover many modular cases without reference to the characteristic of $k$.
  We will finish our discussion of irreducibility of $S^\lambda$ via sharp characterization of the $e \leq n$ case.
  \begin{corollary}
    If $r = 0$, assume $e > 2$.
    Suppose $e \leq n$, and suppose $p > n + r + 1$.
    Then, $S^{(n+r,n)}$ is irreducible if and only if $e \mid r+1$.
  \end{corollary}
  \begin{proof}
    This follows from the proof of Corollary \ref{S irreducibility} part (ii) and the fact that $\nu_p(h) = \nu_p(h')$ for all naturalls $h,h'$. 
  \end{proof}
  \subsection{Branching theorems of Specht modules}
  In this section as well as later sections, we will consider the restriction of representations of $\SH$ to particular subalgebras isomorphic to $\SH_{k,q}\prn{S_{2n + r - 1}}$.
  We verify in Appendix \ref{Algebra} that any two subalgebras of $\SH$ generated by $2n + r - 2$ simple transpositions are canonically isomorphic, and the corresponding restrictions are canonically isomorphic via this isomorphism of algebras.
  We will hence abuse notation, pick one such subalgebra $\SH'$, and notate $\Res_{\SH'}^\SH W$ by $\Res W$ for any $\SH$-module $W$.

@@

  Now that we've characterized how $D^\lambda$ restrict, we can describe how strongly these restrictions characterize irreducibles.
  Namely, we will prove that some $D^\lambda$ having the same composition series as  $D^{(n+r,n)}$ is sufficient to determine that $\lambda = (n+r,n)$ in the case that condition (i) of Corollary \ref{S irreducibility} holds and either $r \neq 0$ or $e \neq 4$.
  \begin{proposition}\label{Combinatorics}
    Let $\lambda$ be an $e$-regular partition of $2n + r$.
    \begin{enumerate}[label={(\roman*)}]
      \item Suppose $r > 0$, suppose $e \nmid r+1, r + 2,\dots,n + r + 1$, and suppose either $e \mid r$ or $e \nmid r-2$.
        If $D^\lambda$ has the composition series 
        \begin{equation}\label{D Composition Series}
          0 \subset D^{(n+r-1,n)} \subset \Res \, D^{\lambda}
        \end{equation}
        with factor $\Res \, D^{\lambda} / D^{(n+r-1,n)} \simeq D^{(n+r,n)}$, then $\lambda = (n+r,n)$.
      \item Suppose $r = 0$, suppose $e \nmid 4$, and suppose $D^{(n,n-1)} \simeq \Res \, D^\lambda$.
        Then $\lambda = (n,n)$. 
    \end{enumerate}
  \end{proposition}
  \begin{proof}
    Note that $e > n$.
    Further, note that the above characterizations are necessary regardless of $e$-regularity;
    in the case that $\mu$ below fails too be $e$-regular, this proposition will prove that $\lambda$ does not satisfy \ref{D Composition Series}, a contradiction.

@@

\section{Crossingless matchings and Specht modules}\label{Crossingless Matchings Section}
In this section, we will analyze the crossingless matchings representation $M := M_{2n + r}^r$ with the goal of proving $M_{2n + r}^r \simeq S^{(n+r,n)}$ under certain conditions in $e$.
We begin by proving irreducibility of $M_{2n + r}^r$ whenever $e \nmid r+2,r+3,\dots,n+r+1$;
when $e>n$, this is true if and only if $S^{(n+r,n)}$ is irreducible by Corollary \ref{S irreducibility}.
This is proven via an inductive process; if $e \nmid n + r + 1$, then $M$ contains no sign subrepresentation, and this allows us to ``project'' down to the case $M_{2(n-1) + r}^r$ and deduce irreducibility of $M$ from irreducibility of this representation.

We will use the following base case to the correspondence throughout:
\begin{lemma}\label{Base cases}
  Note that $S^{(1^n)}$ is the sign representation and $S^{(n)}$ the trivial representation.
  We have the following isomorphisms
  \begin{enumerate}[label={(\roman*)}]
    \item $M_2^0 \simeq S^{(2)}$,
    \item $M_r^r \simeq S^{(1^r)}$.
  \end{enumerate}
  Each of these are 1-dimensional, so they are irreducible.
\end{lemma}
\begin{proof}
  (i) follows from the fact that $(1 + T_1)w = (1 + q)w$, and hence $T_1w = qw$ for any nonzero vector $w \in M_2^0$.
  Similarly, (ii) follows from the fact that $(1 + T_i)w = 0$, so $T_iw = -w$ for any $i$ and any $w \in M_r^r$.
\end{proof}

\subsection{Irreducibility of $M$}
We refer to a vector $w \in M$ satisfying $\SH w = M$ as \emph{cyclic}.
It is a classical result that a representation $W$ is irreducible if and only if every nonzero element of $W$ is cyclic.\cite{Etingof}
We will prove irreducibility by showing that every nonzero $w \in M$ is cyclic;
the following lemma is integral in showing this.

\begin{lemma}
  \label{Cyclic}
  Every basis vector in $M_{2n + r}^r$ is cyclic.
\end{lemma}
\begin{proof}
  We have already proven this in the $r = 0$ case, so suppose that $r > 0$.

  Note that, between anchors at indices $a<a'$ having no arc at index $b$ with $a < b < a'$, the $M_{a'-a}^0$ case allows us to generate the basis vector with all length-2 arcs between $a,a'$ and identical arcs/anchors outside of this sub-matching.
  At the ends, we apply the $M_a^0$ case or the $M_{2n + r - a}^{0}$ case in the same way for the first $a$ or last $2n + r - a$ indices.

  Applying this between each arc gives us a vector with anchors and length-2 arcs, and we may use the appropriate $(1+T_i)$ to move anchors to any positions.
  Then, we may use the reverse process from above to generate the correct matchings between arcs and generate any other basis vector.
\end{proof}

Let $K_{2n+r}^r := \bigcap_{i=1}^{2n+r-1} \ker (1 + T_i) = \ker \bigoplus_{i = 1}^{2n + r - 1} (1 + T_i)$.
This will be an important technical tool in our proof of irreducibility.

\begin{lemma}\label{Trivial}
  Suppose $e \nmid n + r + 1$.
  Then, $K := K_{2n + r}^r = 0$.
\end{lemma}
\begin{proof}[Proof 1.]
  Consider the matrix $A = \bigoplus (1 + T_i)$ having kernel $K$.
  It is sufficient by lemma \ref{Represented} to show that $A$ includes a row $[0,\dots,0,1,0,\dots,0]$ with a nonzero entry only on the row $j$.

@@

  We may prove invertibility of this matrix by proving that $\det B_{n + r} = \brk{n + r + 1}_q$ inductively on $n+r$.
  This is satisfied for our base case $n + r = 1$, so suppose that it is true for each $m < n + r$.
  Then,
  \begin{align*}
    \det B_{n+r} &= (q + 1) \det B_{n + r - 1} - q \det B_{n + r - 2}\\
    &= (q + 1)(1 + \dots + q^{n + r - 1}) - (q + \dots + q^{n + r - 1})\\
    &= 1 + \dots + q^{n + r}\\
    &= \brk{n + r + 1}_q.
  \end{align*}
  Hence $\det B_{n + r} \neq 0$, and $K = 0$.
\end{proof}
\begin{theorem}\label{Irreducibility Theorem}
  Suppose that $e \nmid r+2,r+3,\dots,n+r+1$.
  Then the representation $M_{2n + r}^r$ is irreducible. 
\end{theorem}
\begin{proof}
  We proceed by induction on $n$.
  The base case the base case $n = 0, r \neq 0$ and $n = 1, r = 0$ follow from Lemma \ref{Base cases}.

  Take an arbitrary vector $w \in M$.
  By Lemma \ref{Trivial} there exists some $(1 + T_i) \in \SH$ such that $(1 + T_i)w \neq 0$.
  Note that \[\ima (1 + T_i) = \Span\cbr{w_j \mid w_j \text{ contains the arc }(i,i+1)}.\]
  Hence, as vector spaces, there is an isomorphism $\varphi:\ima(1 + T_i) \rightarrow M_{2(n-1) + r}^r$ ``deleting'' the arc $(i,i+1)$.

  We will show that, for every element $(1 + T_j') \in \SH(S_{2(n-1) + r})$, there is some element $h_j \in \SH(S_{2n + r})$ such that the following commutes:
  \[
    \begin{tikzcd}
      \ima (1 + T_i) \arrow[r,"\varphi" above, "\sim" below] \arrow[d,"h_j"] & M_{2(n-1) + r}^r \arrow[d,"1 + T_j'"]\\
      \ima (1 + T_i) \arrow[r,"\varphi" above, "\sim" below] & M_{2(n-1) + r}^r
    \end{tikzcd}
  \]
  Indeed, when $i+1 \neq j$ this is given by $h_j = 1 + T_j$, and we have $h_{i+1} = q^{-1}(1 + T_i)(1 + T_{i+1})(1 + T_{i-1})$, as given by Figure \ref{bigloop}.

  Note that, by definition, $e \nmid r+2,\dots,n+r$ as well, and hence $(n+r-1,n-1)$ satisfies the hypotheses of the proposition as well.
  Then, by the inductive hypothesis, there is some element $h' \in \SH(S_{2(n-1) + r})$ sending $\varphi((1 + T_i)w)$ to the image of a basis vector of $M_{2n + r}^r$ via $\varphi$;
  then, the action $\SH$ generates the endomorphism $\varphi^{-1}h'\varphi$ of $M$, which sends $(1 + T_i)w$ to a basis vector in $M_{2n + r}^r$.
  This implies that $w$ is cyclic, and hence $M_{2n + r}^r$ is irreducible.
  \begin{figure}
  \begin{adjustbox}{width=\textwidth}
    \Action{6}{1/6, 2/5, 3/4}{2}{1/6, 2/3, 4/5 }{q^{1/2}} \hspace{20pt} 
    \IsoAction{8}{1/8, 2/7, 3/4, 5/6}{3}{1/8, 2/5, 3/4, 6/7}{q^{1/2}}
  \end{adjustbox}
  \begin{adjustbox}{width=\textwidth}
    \Action{4}{1/4, 2/3}{2}{1/4,2/3}{(1 + q)} \hspace{20pt}
    \IsoAction{6}{1/6, 2/5, 3/4}{3}{1/6, 2/5, 3/4}{(1 + q)}
\end{adjustbox}
  \caption{The correspondence between the action of $(1 + T_2)$ on $w'_5 \in M^0_6$ and the action of $q^{-1}(1 + T_3)(1 + T_4)(1 + T_2)$ on the corresponding vector in $M^0_8$ having arc $(3,4)$ first, then on $w'_2 \in M^0_4$.
  This demonstrates that the action works with or without creating a loop.
  }
  \label{bigloop}
  \end{figure}
\end{proof}

\begin{figure}
\[
  \begin{gathered}\CapNAction{4}{1/1,3/2,2/3}{2}\end{gathered}
  \longsquigrightarrow
  \begin{gathered}\BigNAction\end{gathered}
\]
  \caption{The isotopy demonstrating the correspondence between $h_{i+1}$ and $T_i'$;
  the scaling issue with having three simple reflections is handled by the $q^{-1}$ factor in $h_{i+1}$.}
\end{figure}

\subsection{Correspondence with Specht modules}
The following theorem due to Mathas (theorem 5.5 in \cite{Mathas-article}) generalizes the classical branching theorem of the symmetric group.
It will not be necessary for our present proof of the correspondence, but analogy with $M$ is suggestive.
\begin{theorem}[Characteristic-free classical branching theorem]
  Let $\lambda$ be a partition of $m$ with $\ell$ removable nodes.
  Then, $\Res S^\lambda$ has an $\SH_{k,q}(S_{m-1})$-module filtration
  \[
    0 = S^{0,\lambda} \subset S^{1,\lambda} \subset \cdots \subset S^{\ell,\lambda} = \Res S^\lambda
  \]
  such that $S^{t,\lambda} / S^{t-1,\lambda} \simeq S^{\lambda(t)}$ for all $1 \leq t \leq \ell$.\qed
\end{theorem}
In particular, this holds in cases where $S^\lambda$ fails to be irreducible.
If we replace $S^\lambda$ with the appropriate $M_{2n + r}^r$ above, we find the statement of the following proposition.
\begin{proposition}Suppose that $n > 0$.

  \begin{enumerate}[label={(\roman*)}]
    \item
    Suppose that $r > 0$.
    Then, a filtration of $\Res M_{2n + r}^r$ is given by
    \begin{equation}
      0 \subset M_{2n + r - 1}^{r-1} \subset \Res M_{2n + r}^r, \label{Filtration}
     \end{equation}
     with $\Res M_{2n + r}^r / M_{2n + r - 1}^{r-1} \simeq M_{2n + r - 1}^{r + 1}$. 
    \item
      We have the following isomorphism of representations:
      \begin{equation}
        M_{2n - 1}^1 \simeq \Res M_{2n}^0. \label{0 Restriction}
       \end{equation}
  \end{enumerate}
  In the case that $e \nmid r+1,\dots,n + r + 1$, \ref{Filtration} and \ref{0 Restriction} are composition series.
\end{proposition}
\begin{proof}
  \textbf{(i)}
  Note that we may identify the subrepresentation of $\Res M_{2n + r}^r$ having anchor at index $2n+r$ with $M_{2n + r - 1}^{r-1}$.

  Let $U := \Res M_{2n + r}^r / M_{2n + r - 1}^{r - 1}$, and let $\pi: \Res M_{2n + r}^r \twoheadrightarrow U$ be the associated projection to $U$.
  Let $\phi:U \rightarrow M_{2n + r - 1}^{r + 1}$ be the $k$-linear map which regards the arc $(i,2n + r)$ in $U$ as an anchor at $i$ in $M_{2n + r - 1}^{r + 1}$.
  It is not hard to verify that this is a well-defined isomorphism of vector spaces, so we must show that it is $\SH$-linear.

  Given a basis vector $w_j$ containing arc $(i,2n + r)$, $\phi$ is clearly compatible with $(1 + T_{i'})$ with $i' \neq i,i-1$.
  Further, it is easy to verify that $\phi$ is compatible with $T_i$ by definition of the relevant modules, as well as with $(1 + T_{i-1})$ when $w_j$ does not have anchor $i-1$.
  The case that $w_j$ has anchor $i-1$ is illustrated in the following commutative diagram:
  \[
    \begin{tikzcd}
      M_{2n + r}^r \arrow[r,"1 + T_i"] \arrow[d,"\phi \circ \pi"] & M_{2n + t}^r \arrow[r,"\pi"] & U \arrow[d,"\phi"]\\
      M_{2(n-1) + r + 1}^{r+1} \arrow[rr,"1 + T_i"] & & M_{2(n-1) + r + 1}^{r+1}
    \end{tikzcd}
  \]
  which we may diagram chase as follows
    \[
    \QuotDiagram
  \]

  In each of these cases, linearity of $\SH$-action and $\phi$ give 
  \begin{align*}
    \phi(T_jw_i) 
    &= \phi(-w_j + (1+T_j)w)\\
    &= -\phi(w_j) + (1 + T_j)\phi(w_j)\\
    &= T_j\phi(w_j).
  \end{align*}
  Hence $\phi$ is an isomorphism of representations, and the statement is proven.

  \textbf{(ii)}
  This follows from an analogous proof:
  now, $\phi:\Res M_{2n}^0 \rightarrow M_{2(n-1)+1}^1$ is an isomorphism of representaitons, which is proven to be $\SH$-linear by the same proof.
\end{proof}

We've now assembled the basic pieces necessary to prove our correspondence in the case $e > n + r + 1$.

\begin{theorem}\label{Correspondence Theorem}
  Suppose $e > n + r + 1$.
  Then, $M_{2n + r}^r \simeq S^{(n+r,n)}$.
\end{theorem}
\begin{proof}
  The case $n = 0$ is already proven, by lemma \ref{Base cases}, so suppose $n > 0$.
  In order to use Proposition \ref{Combinatorics}, suppose for now that either $e \nmid 4$ or $r > 0$.

  We will prove this inductively; the base case $2n + r = 2$ is implied by \ref{Base cases}, so suppose that $M_{2n + s}^s \simeq S^{(m+s,s)}$ whenever $2m + s < 2n + r$ and $m + s \leq n + r$, so that $e > m + s + 1$.

  Suppose $r > 0$.
  By Theorem \ref{Irreducibility Theorem}, we know that $M_{2n + r}^r \simeq D^\lambda$ for some $e$-restricted partition $\lambda$.
  By the inductive hypothesis and Corollary \ref{S irreducibility}, we have a composition series given by the short exact sequence
  \begin{equation}
    \label{Composition Series} 0 \longrightarrow D^{(n + r - 1,n)} \longrightarrow \Res \, D^\lambda \longrightarrow D^{(n+r,n-1)} \longrightarrow 0
   \end{equation}
  Hence the theorem is given by Proposition \ref{Combinatorics} (i).
